Multi-EWAS enrichment example

### 2024-01-18 figs/multi_ewas_example.Rmd
reports not needed

r1 <- lapply(1:length(l1),function(i) {
  name=names(l1[i])
  m <- l1[[i]]
  m2 <- mitch_import(x=m,DEtype="prescored",geneTable=gt,geneIDcol="CpG")
  mres <- mitch_calc(x=m2,genesets=gs_symbols,minsetsize=5,cores=2, priority="significance")
  mtable <- mres$enrichment_result
  mitch_report(res=mres,outfile=paste("mitchreport_prev_",name,".html",sep="",overwrite=TRUE))
})

>>>>

r1 <- lapply(1:length(l1),function(i) {
  name=names(l1[i])
  m <- l1[[i]]
  m2 <- mitch_import(x=m,DEtype="prescored",geneTable=gt,geneIDcol="CpG")
  mres <- mitch_calc(x=m2,genesets=gs_symbols,minsetsize=5,cores=2, priority="significance")
  mtable <- mres$enrichment_result
  #mitch_report(res=mres,outfile=paste("mitchreport_prev_",name,".html",sep="",overwrite=TRUE))
})
